---
title: "Seattle Airbnbs Project"
author: "Karl Yang, Lin He, Peihuan Han, John Wang"
date: "5/20/2019"
output: html_document
css: styles.css
---

```{r echo = FALSE, message = FALSE}
# Load libraries
library("knitr")
library("kableExtra")
source("scripts/chart1.R")
source("scripts/chart2.R")
source("scripts/chart3.R")
source("scripts/tables.R")

# Load dataset
airbnb <- read.csv("data/seattle-airbnb/listings.csv", stringsAsFactors = FALSE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

## Introduction

## Summary

## Summary Table by Room Types
Do you know which room type in Airbnb is most popular one in Seattle area? Which room type is the most expensive one? And which room type gives the best experience? To answer these question, we will create a summary table by grouping the airbnb rooms according to their room type so we can compare the difference between each room type easily!
```{r}
summary_by_type_table(airbnb)
```

From the table above, we can see that the most popular room type of Airbnb in Seattle is definitely the entire home or the entire apartment, with the most number of rooms available and the largest number of reviews. Besides, it also has the highest rate of instant bookable rooms. However, it's also the most expensive type of room, with both the highest mean price and highest cleaning fee. We can see its mean price is twice as much as Private rooms' and three times as much as Share rooms.

So with the highest price and the most popularity, does the entire home/apartment also gives the best living experience? The data above tells us it's not really true. In fact, from the table above we can see that private rooms' mean rating is slightly higher than the entire home/apartment. Therefore, if you plan to travel Seattle with 1 or 2 persons, maybe private room is a good choice with good experience and cheaper prices; if you plan to travel with your entire family or lots of friends together, renting the entire home/apartment may be a good choice.


## All Airbnb Listings
Want to see all the listing on a map? Not problem! You can find all the 
listings below. You can get a good sense of the geographical 
distributon of the Airbnb listings in Seattle. A lot of listings are 
clustered in downtown seattle. You may find a lot of choice over there. 
You can click on the listing if you want to find more information. 
The popup window will provides you a thrumbnail image of the listing along 
with other useful information. If you want to find out more about the listing, 
you can click on the link which will bring you to Airbnb!

```{r, echo=FALSE, message=FALSE}
chart1(airbnb)
```

## Price
One bedroom house could not satisify you? Or you are coming with a large group. 
No problem! We will give you the pricing distribution divided by the number of 
bedrooms that allows you to make a better choice based on you budget. 
You are free to pick the number of bedrooms that best fits your need. 

```{r, echo=FALSE, message=FALSE}
chart2(airbnb)
```

## Best Neighbourhoods
What? Budget is not a concern for you? You want the best of best experience. 
We have selcted five top-rating neigbourhood for you. You can activily look for 
places to stays in those communities. 

```{r, echo=FALSE, message=FALSE}
chart3(airbnb)
```
