---
title: "Seattle Airbnbs Project"
author: "Karl Yang, Lin He, Peihuan Han, John Wang"
date: "5/20/2019"
output: html_document
css: styles.css
---

```{r echo = FALSE, message = FALSE}
# Load libraries
library("knitr")
library("kableExtra")
source("scripts/chart1.R")
source("scripts/chart2.R")
source("scripts/chart3.R")
source("scripts/tables.R")

# Load dataset
airbnb <- read.csv("data/seattle-airbnb/listings.csv", stringsAsFactors = FALSE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

## Introduction

## Summary

## Table
```{r}
top_airbnb_table(airbnb)
```

## All Airbnb Listings
Want to see all the listing on a map? Not problem! You can find all the 
listings below. You can get a good sense of the geographical 
distributon of the Airbnb listings in Seattle. A lot of listings are 
clustered in downtown seattle. You may find a lot of choice over there. 
You can click on the listing if you want to find more information. 
The popup window will provides you a thrumbnail image of the listing along 
with other useful information. If you want to find out more about the listing, 
you can click on the link which will bring you to Airbnb!

```{r, echo=FALSE, message=FALSE}
chart1(airbnb)
```

## Price
One bedroom house could not satisify you? Or you are coming with a large group. 
No problem! We will give you the pricing distribution divided by the number of 
bedrooms that allows you to make a better choice based on you budget. 
You are free to pick the number of bedrooms that best fits your need. 

```{r, echo=FALSE, message=FALSE}
chart2(airbnb)
```

## Best Neighbourhoods
What? Budget is not a concern for you? You want the best of best experience. 
We have selcted five top-rating neigbourhood for you. You can activily look for 
places to stays in those communities. 

```{r, echo=FALSE, message=FALSE}
chart3(airbnb)
```
